\thesistitle

### 2019-08-25 sections/research.tex
Research

\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
Clone type 1-3 (see Section~\ref{chap:backgroundclonetypes}) can (and should) not always be automatically refactored. In Section~\ref{sec:literaturetypeproblems} we list shortcomings of each clone type that invalidate refactoring opportunities. In Section~\ref{sec:rtypes} we propose new clone type definitions that address these shortcomings.

@@

Type 1 clones are implemented as textual equality between code fragments (except for whitespace and comments) by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating}. Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases, refactoring opportunities could be invalidated. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone. %When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error-prone and can result in an uncompilable project or a difference in functionality.

@@

>>>>

\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
Clone type 1-3 (see Section~\ref{chap:backgroundclonetypes}) cannot always be automatically refactored. In Section~\ref{sec:literaturetypeproblems} we list shortcomings of each clone type that invalidate automated refactoring opportunities. In Section~\ref{sec:rtypes} we propose new clone type definitions that address these shortcomings.

@@

@@

Type 1 clones are implemented as textual equality between code fragments (except for whitespace and comments) by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating}. Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases, refactoring opportunities could be invalidated. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
